### 2015-07-07 paper.tex
optimize the part: Muon estimation

		Cosmic muon rays can also produce a large number of neutrons
		in the rock around central,these neutron can produce fast 
		neutron background in the central detector. If water shield
		thickness is 2.5 meters in JUNO, fast neutron ratio is 0.3\%,
		considering detector volume and geometry effects.

>>>>

		The remaining energy cosmic muon rays can also produce a large number of neutrons
		in the rock around central detector,these neutron can produce fast 
		neutron background in the central detector. In order to shield the neutrons and the
		natural radioactivity in the rock, 2.5m meter thickness water is used for shielding.
